Reconstructing Propositional Proofs in Type Theory

### 2017-12-06 paper/sections/proof-reconstruction.tex
[ paper ] formalization pattern with some fixes.

@@

\begin{equation*}
  \text{If }Γ ⊢ φ \text{ then }Γ ⊢ \fun{metisRule}~φ~ψ, \text{ where } ψ : \Target.
\end{equation*}

@@

The remainder of this section will be devoted to present a formal
description in type theory of each rule presented in
Table~\ref{tab:agda-metis-table} using the pattern present in the
example above.  We follow the same order to present the rules as the
table shows.

>>>>

As we mention in the beginning of this section, to reconstruct
the \Metis inference rules, we use the following pattern in
the formalization.

@@

\begin{equation*}
  \text{If }Γ ⊢ φ \text{ then }Γ ⊢ \fun{metisRule}~φ~ψ\enspace.
\end{equation*}

@@

The remainder of this section will be devoted to present a formal
description in type theory of remaining \Metis rules presented in
Table~\ref{tab:agda-metis-table} using the pattern presented in the
example above. We follow the same order to present the rules as the
table shows.
